A Simple Type Theory for Category Theory

### 2022-02-15 paper/lipics-v2021-sample-article.tex
start the interpretation part

@@

\begin{definition}
  For any $\Gamma \isadtctx$, we construct a virtual double category
  $V^\Gamma$.
  \begin{enumerate}
  \item $V^\Gamma_v$ is the set of terms $\Gamma \vdash \cat C \isaCat$.
  \item $V^\Gamma_v(\cat C, \cat D)$ is the set of objects $\Gamma
    \pipe \alpha:\cat C \vdash a : \cat D$.
  \item $V_h$ is the set of triples $(\cat C, \cat D, \Gamma \pipe \alpha:\cat C;\beta:\cat D \vdash R \isaSet)$
    where $d^\pm$ are the projections
  \item $V^\Gamma_h(\vec R; S)$ is the set of triples $(a,b,\Gamma
    \pipe \Phi \vdash t : S[a;b])$ where $\Phi$ is the context
    corresponding to $\vec R$ and $d^\pm$ are the obvious projections.

  \item The identity morphisms are $(\cat C, \cat D, R)$ is $\Gamma\pipe\alpha:\cat C, x:R\beta:\cat D \vdash x:R$
  \item Composition $(a,b,t) \circ [(a_1,),\ldots]$ is given by
    substitution in each component: $(a[a_1],b[a_n], t[\phi])$.
  \item associativity and unit rules for composition follow by the
    definition of substitution.
  \end{enumerate}
\end{definition}

>>>>

\subsection{Category of Signatures and Models}

Our goal is to establish that the syntax of SCT (with whichever type
constructors we choose) presents a free virtual double category (with
the appropriate universal properties). To start we define appropriate
categories of signatures and double categories.

\begin{definition}
  Define the category Sig to have as objects well-formed contexts
  $\Gamma$ and morphisms $\gamma : \Delta \to \Gamma$ morphisms of
  contexts, with the composition as substitution and identity as a
  context morphism of all variable references.
\end{definition}

Second, there is a category of virtual double categories and functors.

\begin{definition}
  A morphism of virtual equipments with blah is a functor of virtual
  double categories that strictly preserves the universal properties.
\end{definition}

Next, we define a profunctor between the category of signatures and
the category of virtual equipments.

\begin{definition}
  Given a well-formed signature $\Gamma$ and a virtual equipment
  $\mathcal V$, we mutually define the following notions:

  \begin{itemize}
  \item The set $\sem{\Gamma}_{\mathcal V}$
  \item For any $\Gamma \vdash A$ and $\gamma \in \sem{\Gamma}_{\mathcal V}$, a set $\sem{A}_{\mathcal V} \gamma$
  \item For any $\Gamma \vdash M : A$ and $\gamma \in \sem{\Gamma}_{\mathcal V}$, an element $\sem{M}_{\mathcal V} \in \sem{A}_{\mathcal V} \gamma$
  \item categories...
  \item functors...
  \item profunctors...
  \item trans contexts,
  \item transformations
  \end{itemize}

  An interpretation of a signature $\Gamma$ in a virtual equipment
  $\mathcal V$, $\textrm{Interp}(\Gamma,\mathcal V)$ is an element of
  the set $\sem{\Gamma}_{\mathcal V}$ where we mutually define the set

  \begin{align*}
    \sem{\cdot}_{\mathcal V} &= 1\\
    \sem{\Gamma, x:A}_{\mathcal V} &= \sum_{\gamma \in \sem{\Gamma}_{\mathcal V}} \sem{A}_{\mathcal V}\gamma\\
  \end{align*}

  with an 
  \begin{align*}
    \sem{\Gamma, x:A}_{\mathcal V} &= \sem{\Gamma}_{\mathcal V} \times \sem{A}_{\mathcal V}\\
    \sem{\Gamma}_{\mathcal V} &= 1\\\\
    \sem{\Sort}_{\mathcal V} &= \mathcal V_0\\
    \sem{\varr{\cat C}{\cat D}}_{\mathcal V} &= \mathcal V_v(\sem{\cat C})
  \end{align*}

\begin{definition}
  For any $\Gamma \isadtctx$, we construct a virtual double category
  $V^\Gamma$.
  \begin{enumerate}
  \item $V^\Gamma_v$ is the set of terms $\Gamma \vdash \cat C \isaCat$.
  \item $V^\Gamma_v(\cat C, \cat D)$ is the set of ``objects'' $\Gamma
    \pipe \alpha:\cat C \vdash a : \cat D$. The category structure is
    given by substitution, with the variable $\alpha \vdash \alpha$
    the identity.
  \item $V_h$ is the set of triples $(\cat C, \cat D, \Gamma \pipe \alpha:\cat C;\beta:\cat D \vdash R \isaSet)$
    where $d^\pm$ are the projections
  \item $V^\Gamma_h(\vec R; S)$ is the set of triples $(a,b,\Gamma
    \pipe \Phi \vdash t : S[a;b])$ where $\Phi$ is the context
    corresponding to $\vec R$ and $d^\pm$ are the obvious projections.

  \item The identity morphisms are $(\cat C, \cat D, R)$ is $\Gamma\pipe\alpha:\cat C, x:R\beta:\cat D \vdash x:R$
  \item Composition $(a,b,t) \circ [(a_1,),\ldots]$ is given by
    substitution in each component: $(a[a_1],b[a_n], t[\phi])$.
  \item Associativity and unit rules for composition follow from the
    definition of substitution by a straightforward induction.
  \end{enumerate}
\end{definition}

@@

Let $$
